\subsection*{August 2021--December 2023}

\textit{Senior Backend Developer, Team Leader at the Operation Portal
team at KLM, \href{https://klm.nl}{\url{klm.nl}}, Amsterdam, The
Netherlands}

My goal was to design and develop new features of Operation
Portal. Mentor junior developers. Organise standby support and
educate the team. Manage project instrumentation and optimization,
make it more robust.  Develop database schema migration scripts. And
lastly, curate the process of migration to the Cloud.

Product was started as a proof-of-concept at the beginning of the
Corona crisis and was built with Scala and TypeScript on top of HBase,
GraphQL and React. It supports flights and passengers scheduling
operations with close to real time data updates.

Most of my contribution was to portal's backend, but I also have
created many pull-requests to our frontend and different other teams'
projects, working with Scala and Python.

During my work at KLM, I designed and implemented multiple developer
tools and CI/CD pipelines:
\begin{itemize}[noitemsep, nosep]
  \item Security checks pipelines
  \item Public Docker images adoption framework
  \item Grafana dashboards-as-a-code system
\href{https://github.com/aleksandr-vin/grafana-dashboards-provisioning}{\url{github.com/aleksandr-vin/grafana-dashboards-provisioning}}
  \item Created proof-of-concept of a scalable REST API service for
proprietary costs calculation library
  \item Created KLM Abbreviations Dictionary (an Apple Dictionary)
  \item Created VR application of Operations Control Center building
for proof-of-concept of new information screens (in Blender, Unity and
Oculus Quest 2)
\end{itemize}
