\subsection*{November 2019--July 2020}

\textit{Team Lead at StackState,
\href{https://stackstate.com}{\url{stackstate.com}}, Utrecht, The
Netherlands}

StackState is a product company of Xebia Group. It was founded in
2015. I joined the company as Senior Backend Developer in May 2019
with the goal to take Team Leader's role in 6 months. In September
2019 StackState was named a Cool Vendor by Gartner.

After initial 6 months of work in the company I took the Team Leader
role of feature delivering team of 6 people, including me and a Scrum
Master.  Two of the developers were working remotely, one in the -6
hours time zone. During these initial months I set up 1:1 calls with
all team members, took initiative and proved to be a support and
mentor for the team. During the whole period of work in StackState I
was mentored by my manager and held 1:1 meetings with him on a
bi-weekly basis. With the strike of corona-crisis we transformed our
process to completely remote-working one, while still being able to
successfully deliver on the goals that team committed.

My responsibilities were: organization and maintenance of the team,
team focus on deliverables and goals, mentoring team-members, spotting
and resolving team problems and escalating when needed.

At the end of June the company made a decision to cut down costs and
close the team, letting us go.

I was participating in delivering 4 major releases of the product.

With the Team Leader's role I was also having a Release Manager's role
to organize, control and teach other developers of the release
process, also to prioritize improvements to that process automation.
