\subsection*{August 2016--April 2019}

\textit{Senior Backend Developer at Veon,
\href{https://veon.com}{\url{veon.com}}, Amsterdam, The Netherlands}

Veon is a big multinational company, formerly known as Vimpelcom, that
has different telcos across the globe. I joined the company in its
journey of digital transformation, helping to develop Engagement
Platform with the goal to become a content provider as well as a
service provider.

\subsubsection*{Last project (mid 2018--beg 2019)}

Leading Core Experience, Identity \& Safety team of 5 backend
developers (including myself), 4 Android and 4 iOS developers
(partially remote). Along with the support of onboarding,
authentication, management of the platform users and their consents,
the team is busy with removing/refactoring legacy backbone code that
was built at the very beginning of the platform by a third party. That
required coordinated work across all the teams and proper planning and
execution on the running platform. As a side project for part of the
team, we are designing and prototyping a generic search service to
support full text search in different aspects of the platform. The
engine is Elasticsearch and Kafka. We are using the same common stack
of technologies that we already used in previous projects in the
company.

\subsubsection*{Third project (end 2017--mid 2018)}

Designing, estimating and developing Consents Management Service with
mobile SDK. In scope of GDPR adoption, I designed a service to manage
consents versions and track users' decisions. Service supports
different locales of a consent text, filtering by user's attributes,
versioning of legal meaning of the consent and smart invalidation of
user's decisions. Service utilizes HTTP caching to reduce client
requests to a reasonable amount. Uses Akka Streams to perform batch
import/export operations with failovers. Supports event-driven
operations.  To implement the service I gathered and led a small team
of 1 more backend and 2 mobile app developers. We were using the same
stack of technologies as in previous projects.

\subsubsection*{Second project (mid 2017--end 2017)}

Participation in Platform team. Our goal was to optimize and develop a
common layer of our microservices, working closely with our
infrastructure team. We moved from heterogeneous to homogeneous Akka
clusters with sharding, and introduced event driven architecture with
Kafka. We applied monitoring of our services with the help of Kamon
framework and developed Grafana dashboards. For benchmarking we used
Gatling and JMeter as well as Java Microbenchmark Harness,
Elasticsearch and Python. During this project, while working close to
the infrastructure team, I developed some automation and monitoring
command line tools using Python, Bash, Scala scripting with Ammonite,
ssh tunneling, docker and psql util.

\begin{itemize}[noitemsep, nosep]
  \item \textbf{Languages:} Scala, Python, Bash
  \item \textbf{Frameworks/Libraries:} Akka Actors, Akka HTTP, Akka
Streams, Akka Cluster, Kamon, Slick, Flyway Migrations, Protobuf,
ConstructR, Scala Test, Scala Check, Scala Mock, Mockito, Swagger
  \item \textbf{Services:} Kafka, Elasticsearch, Consul, Kong API
Gateway
\end{itemize}

\subsubsection*{First project (mid 2016--mid 2017)}

Developing Identity Management services from scratch, responsible for
onboarding, authentication and managing of the users. Initially the
flow was supported by third party services, and our goal was to move
the backend support to our site in steps that required API design with
mobile app developers, integration across AWS locations and design of
appropriate strategy to execute the migration. Also we set up
Elasticsearch stack at that time and embraced structured logging,
brought unit testing and set up integration testing with the help of
Docker Compose.  Applied code review process in our merge
requests. Frankly speaking, we've set up the team culture.

\begin{itemize}[noitemsep, nosep]
  \item \textbf{Languages:} Scala, Python, Bash
  \item \textbf{Frameworks/Libraries:} Akka Actors, Akka HTTP, Akka
Cluster, Slick, Flyway Migrations, Scalaz, Argonaut, Spray, ScalaTest,
ScalaCheck, ScalaMock, Mockito, Swagger
\end{itemize}
